\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-21 document/XSGRB_sample.tex

\usepackage[stable]{footmisc}
\usepackage{graphicx}
\usepackage{txfonts}
%\usepackage{hyperref}
\usepackage{natbib}
\bibpunct[, ]{(}{)}{;}{a}{}{,}
%\bibliographystyle{./bibtex/apj}

\newcommand{\farc}{\hbox{$.\!\!^{\prime\prime}$}} 
\newcommand{\ergA}{$\rm{erg\,cm^{-2}\,s^{-1}\,\AA^{-1}}$} 
\newcommand{\erg}{$\rm{erg\,cm^{-2}\,s^{-1}}$} 
\newcommand{\kms}{$\rm{km\,s^{-1}}\,$}
\newcommand{\hb}{H$\beta$} 
\newcommand{\ha}{H$\alpha$}
\newcommand{\hg}{H$\gamma$} 
\newcommand{\hi}{\mbox{H\,{\sc i}}} 
\newcommand{\oi}{[\ion{O}{2}]} 
\newcommand{\sii}{[\ion{S}{2}]} 
\newcommand{\oii}{[\ion{O}{2}]} 
\newcommand{\oiii}{[\ion{O}{3}]}
\newcommand{\nii}{[\ion{N}{2}]} 
\newcommand{\hii}{$\rm{H}_2$}
\newcommand{\griz}{$g' r' i' z'$}
\newcommand{\JHK}{$JHK_{\rm{s}}$}
\newcommand{\gK}{$g' r' i' z' JHK_{\rm{s}}$}
\newcommand{\Msun}{$M_\odot$}

\begin{document}

@@

	\author{
		J.~Selsing\altaffilmark{1}, 
		D.~Malesani\altaffilmark{1}, 
		P.~Goldoni\altaffilmark{14}, 
		J.~P.~U. Fynbo\altaffilmark{1}, 
		A.~de~Ugarte~Postigo\altaffilmark{11}, 
		J.~Japelj\altaffilmark{20},
		P.~D'Avanzo,
		Z.~Cano,
		S.~Covino\altaffilmark{10}, 
		V.~D'Elia\altaffilmark{7, 12}, 
		H.~Flores,
		O.~E.~Hartoog\altaffilmark{6},
		J.~Hjorth\altaffilmark{1}, 
		P.~Jakobsson\altaffilmark{5}, 
		T.~Kr\"{u}hler\altaffilmark{1}, 
		A.~Levan,
		A.~Melandri,
		S.~Piranomonte \altaffilmark{7},
		R.~S\'anchez-Ram\'irez\altaffilmark{11},
		S.~Schulze\altaffilmark{17, 18}, 
		N.~R.~Tanvir\altaffilmark{19},
		C.~Th{\"o}ne,
		S.~D.~Vergani\altaffilmark{7, 8},
		P.~M.~Vreeswijk\altaffilmark{3}, 
		D.~J.~Watson\altaffilmark{1},
		K.~Wiersema\altaffilmark{19},
		D.~Xu\altaffilmark{1}
		L.~Christensen\altaffilmark{1},
		A.~De~Cia\altaffilmark{3}, 
		L.~Kaper\altaffilmark{6}, 
		L.~A.~Antonelli,
		F.~Fiore,
		A.~Gomboc,
		P.~Groot,
		F.~Hammer,
		C.~Ledoux\altaffilmark{2}, 
		E.~Maiorano,
		B.~Milvang-Jensen\altaffilmark{1}, 
		E.~Palazzi,
		E.~Pian,
		J.~Schaye,
		G.~Tagliaferri\altaffilmark{7},
		R.~A.~M.~J.~Wijers\altaffilmark{6}
	}

@@

			(1) \citet{Antonio090313}; (2) This work ; (3) Skuladottir (2010);
			(4) \citet{Valerio090926A}; (5) \citet{Klaas091018}; (6) \citet{Vergani091127,Cobb091127}; 
			(7) \citet{christina100219A}; (8) \citet{Buffano} ; (9) de Ugarte Postigo et al. ;
			(10) \citet{Haartog100901A}; (11) \citet{Sparre101219B}; (12) \citet{Sparre111008A};
			(13) \citet{Levanultralong}; (14) D'Elia et al., submitted; (15) \citet{SchulzeSNGRB};
			(16) \citet{Kruehler120815A}; (17} \citet{friis121024A}

@@

>>>>

\usepackage[stable]{footmisc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{txfonts}
%\usepackage{hyperref}
\usepackage{natbib}
\bibpunct[, ]{(}{)}{;}{a}{}{,}
%\bibliographystyle{./bibtex/apj}

\newcommand{\farc}{\hbox{$.\!\!^{\prime\prime}$}} 
\newcommand{\ergA}{$\rm{erg\,cm^{-2}\,s^{-1}\,\AA^{-1}}$} 
\newcommand{\erg}{$\rm{erg\,cm^{-2}\,s^{-1}}$} 
\newcommand{\kms}{$\rm{km\,s^{-1}}\,$}

\newcommand{\griz}{$g' r' i' z'$}
\newcommand{\JHK}{$JHK_{\rm{s}}$}
\newcommand{\gK}{$g' r' i' z' JHK_{\rm{s}}$}
\newcommand{\Msun}{$M_\odot$}
\newcommand{\lya}{Ly$\alpha$} 
\newcommand{\lyb}{Ly$\beta$} 
\newcommand{\hb}{H$\beta$} 
\newcommand{\ha}{H$\alpha$} 
\newcommand{\oi}{[\ion{O}{1}]} 
\newcommand{\sii}{[\ion{S}{2}]} 
\newcommand{\oii}{[\ion{O}{2}]$\lambda$3727} 
\newcommand{\oiii}{[\ion{O}{3}]$\lambda$5007}
\newcommand{\nii}{[\ion{N}{2}]} 
\newcommand{\feii}{\ion{Fe}{2}} 
\newcommand{\civ}{\ion{C}{4}} 
\newcommand{\cii}{\ion{C}{2}}
\newcommand{\mgii}{\ion{Mg}{2}} 
\newcommand{\hi}{\ion{H}{1}} 
\newcommand{\ali}{\ion{Al}{1}} 
\newcommand{\SIii}{\ion{Si}{2}} 
\begin{document}

@@

	\author{
		J.~Selsing\altaffilmark{1}, 
		D.~Malesani\altaffilmark{1}, 
		P.~Goldoni\altaffilmark{14}, 
		T.~Kr\"{u}hler\altaffilmark{1}, 
		J.~P.~U. Fynbo\altaffilmark{1}, 
		A.~de~Ugarte~Postigo\altaffilmark{11}, 
		J.~Japelj\altaffilmark{20},
		P.~D'Avanzo,
		Z.~Cano,
		S.~Covino\altaffilmark{10}, 
		V.~D'Elia\altaffilmark{7, 12}, 
		H.~Flores,
		O.~E.~Hartoog\altaffilmark{6},
		J.~Hjorth\altaffilmark{1}, 
		P.~Jakobsson\altaffilmark{5}, 
		A.~Levan,
		A.~Melandri,
		S.~Piranomonte \altaffilmark{7},
		R.~S\'anchez-Ram\'irez\altaffilmark{11},
		S.~Schulze\altaffilmark{17, 18}, 
		N.~R.~Tanvir\altaffilmark{19},
		C.~Th{\"o}ne,
		S.~D.~Vergani\altaffilmark{7, 8},
		P.~M.~Vreeswijk\altaffilmark{3}, 
		D.~J.~Watson\altaffilmark{1},
		K.~Wiersema\altaffilmark{19},
		D.~Xu\altaffilmark{1}
		L.~Christensen\altaffilmark{1},
		A.~De~Cia\altaffilmark{3}, 
		L.~Kaper\altaffilmark{6}, 
		L.~A.~Antonelli,
		F.~Fiore,
		A.~Gomboc,
		P.~Groot,
		F.~Hammer,
		C.~Ledoux\altaffilmark{2}, 
		E.~Maiorano,
		B.~Milvang-Jensen\altaffilmark{1}, 
		E.~Palazzi,
		E.~Pian,
		J.~Schaye,
		G.~Tagliaferri\altaffilmark{7},
		R.~A.~M.~J.~Wijers\altaffilmark{6}
	}

@@

			(1) \citet{DeUgartePostigo2010}; (2) This work ; (3) Skuladottir (2010);
			(4) \citet{DElia2010}; (5) \citet{Wiersema2012}; (6) \citet{Vergani2011, Cobb2010}; 
			(7) \citet{Thone2013}; (8) \citet{Bufano2011} ; (9) \citet{DeUgartePostigo2011} ;
			(10) \citet{Hartoog2013}; (11) \citet{Sparre2011}; (12) \citet{Sparre2014};
			(13) \citet{Levan2014}; (14) \citet{DElia2014}; (15) \citet{Schulze2014};
			(16) \citet{Kruhler2013}; (17} \citet{Friis2015}

@@

	\subsection{GRB120327A (z = 2.813)}
	The data presented here also formed the basis of GCN \#
	13134\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/13134.gcn3}} and is published
	in \citet{DElia2014}.
	Consisting of two observations, 2.13 hrs and 29.98 hrs after the burst,
	continuum is visible in all arms for both.
	Absorption features from Ly-limit, \lya, \cii/\cii$^*$, \SIii/\SIii$^*$, \ali,
	\feii ~and \mgii ~are detected at a consistent redshift, $z = 2.813$.
